\insertcvheader

\clrecipient
 {M. Jean-François Yelle}
 {Managing Director}
 {Maxon Computer Canada Inc.}
 {434 Saint-Pierre st. \#400}
 {Montreal, QC, H2Y 2M5}
 
\cllocationdate
 {Montreal}
 {January 9th}
 
\clgreeting
 {Dear Mr. Yelle}
 
As I have recently completed my master's degree at Polytechnique of Montreal, I am currently looking for a job in 3D or 2D rendering as a software developer. You may note that, at the end of my studies, I have obtained a job at Autodesk to work on the last month of an architecture visualization project, which greatly confirmed my passion for computer graphics.

Two open positions at Maxon really caught my attention. The first, and the one for which I may be the most qualified for, is \textit{Junior C++ Developer (Modeling)}. Even though I may introduce myself as a junior developer, I have already earned a great amount of experience in modeling and rendering. From my resume, you will see that the subject of my master's thesis was numerical fluid mechanics mesh generation and adaptation on the GPU. You may also notice that I have acquired experience with analytic and parametric surfaces through my numerous personal projects and some of my master's classes~: \textit{Computer Aided Geometric Design and Visualization}, \textit{Advanced Computer Graphics} and \textit{Finite Elements Mathematics}. Since the beginning my studies, I keep myself aware of C++'s and OpenGL's latest developments by integrating their new features into my projects. I also look forward to adding Vulkan to my areas of expertise. 

The second open position that particularly caught my attention is \textit{GPU Rendering Specialist}. My long term career goal is to work on a production path tracer. As you will notice, my most ambitious personal project consisted in the development of a unidirectional path tracer in conjunction with a software suite to visualize, in real time, animate and apply post production effects on short films. The rendering was done in parallel and distributed on multiple computers. This software suite enabled me to produce a short animated film: \textit{The Fruit -- A moving Picture}. This project made me learn a lot about offline rendering, however, without really giving a sound theoretical basis. That is why I have decided to study photo-realistic rendering more seriously by making \textit{Physically Based Rendering: From Theory to Implementation} my bedside book.
 
In addition to my experience and motivation, I think you will be interested to hear that I am a great team member. Almost every job I have occupied to this day has been managed under agile principles and I loved the type of interactions that it brought in the teams. I short, teamwork suites me as well as individual work.

I am available for an interview at your convenience. Please do not hesitate to browse my résumé below.

Thank you for your consideration,

\clsignature{William Bussière}