Dear Mr. Wiazowski,

As I have recently completed my master's degree at Polytechnique Montreal, I am currently looking for a job in 3D rendering as a software developer. You may note that, at the end of my studies, I have obtained a job at Autodesk to work on the last month of an architecture visualization project, which greatly confirmed my passion for computer graphics.

I am much more of a photography and cinematography enthusiast than a hard core gamer, but cannot stop myself from enjoying how real time rendering has become beautiful and realistic in the last few years. I have learned physically based rendering through personal projects on global illumination and I am pleased to see that the game industry is widely embracing the same principles in their renderers. During my short stay at Autodesk, I had the chance to work on a modern game engine that supported all the latest game consoles and platforms. This gave me a glimpse of a good architecture to support multiple shading languages (GLSL, HLSL, PSSL, Metal) and multiple rendering libraries. I have also been exposed to some advanced rendering techniques like deferred shading, clustered shading, cascaded shadow mapping and GPU light baking.

Be assured that I am a great philomath. For at last ten years, I could not stop myself from developing computer simulations of 2D computational fluid mechanics, global illumination (path tracing), 2D rigid body mechanics, water surface waves, etc. Learning new mathematics never stopped me from elaborating new personal projects. Also note also that most of those programs were written in C++.

In terms of game development, I know the basics and I am ready to learn more. I started coding with Game Maker in my secondary school years and managed to complete several mini games of different genre. More recently, for our last integrator project at Polytechnique, my team designed, developed and presented an obstacle course for the Kinect 2 at Laval Virtual. The game was made with Unity and included an Android companion app for allies and ennemies to interact with the obstacle course. With that said, as you are recruiting a 3D rendering programmer, you might be more interested in someone who would be able to improve your rendering pipeline, and that's what I can offer you.

I am available for an interview at your convenience. Please do not hesitate to browse my résumé.

Thank you for your consideration,

William Bussière
